Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-15 main.tex
Made a lot of changes to notation Started on writing the filter section properly - intro bit done - measurement function requirements done (and merged into intro bit - started on the observation model modification section - redid the big equations with new notation

The navigator state is defined as 
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & dx & y & dy
    \end{bmatrix}^\top\,.
\end{equation}
A known process model is followed, which at time $k$ is given by
\begin{equation}
    \mean{x}_k = \vec{f}(\mean{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
\end{equation}
with zero-mean Gaussian process noise $w_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
\begin{equation}
    z_k = h_i(\mean{x}_k)+\rv{v}_k\,, \label{eqn:measurement_model}
\end{equation}
with noise $\rv{v}_k \sim \mathcal{N}(\vec{0},\mat{R})$, while the measurement function $h_i$, for sensor $i$ at location
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        x_{i} & y_{i}
    \end{bmatrix}^\top\,,
\end{equation} 
is defined as
\begin{equation}
    \begin{split}
        h_i(\mean{x}_k) &= \left\|
        \begin{bmatrix}
            \mean{x}_{k[0]} \\
            \mean{x}_{k[2]}
        \end{bmatrix}
        - \vec{s}_{i}\right\| \\
        &= \sqrt{(\mean{x}_{k[0]}-x_{i})^2 + (\mean{x}_{k[2]}-y_{i})^2}\,.
    \end{split}
\end{equation}
We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\mean{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $z_k$ at any time $k$.

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of state estimate $\mean{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
\begin{equation}
    \mean{y}_k = \mat{P}_k^{-1}\mean{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \mean{y}_k = \mean{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobian
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\mean{x}_k} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\mean{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
\begin{equation}
    \mean{x}_k = \mat{Y}_k^{-1}\mean{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \mean{x}_k = \vec{f}(\mean{x}_{k-1})
\end{equation}
and
\begin{equation}
    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\mean{x}_k}\,.
\end{equation}

@@

\section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
Given our definitions for the aggregation scheme in Section \ref{sec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}. We consider a navigator in the presence of $n$ range sensors, running a local filter with update steps computed by equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}. Received information from each sensor $i$ consists of the measurement vector
\begin{equation}
    \vec{i}_i = \mat{H}^\top_{k,i} \mat{R}^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k)
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_i = \mat{H}^\top_{k,i} \mat{R}^{-1}_i \mat{H}_{k,i}\,,
\end{equation}
at each time step $k$. All sensitive sensor information is captured exclusively in the filter by the Products $\vec{i}_i$ and $\mat{I}_i$, namely their measurements $z_{k,i}$, measurement variances $\mat{R}_i$ and locations, captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$. Encryption of $\vec{i}_i$ and $\mat{I}_i$ at the sensors would, however, disclose the location information of $\mean{x}_k$, required for computing Jacobians $\mat{H}_{k,i}$ in \eqref{eqn:measurement_jacobian}.

@@

% Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?

% Explain how leakage of the final aggregation sum to the navigator means leakage of the average sensor location and measurement to the navigator. This is the reason for the acceptance of this leakage, as we pointed out in the problem statement section.

We wish to encrypt current state information and use the encryption scheme defined to compute measurement information $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ as a linear combination of said state information, and encrypt it for aggregation. This then allows the navigator to learn only the sums $\sum^n_{i=1}H^\top R^{-1}_i(z_i - h(x) + Hx)$ and $\sum^n_{i=1}H^\top R_i^{-1}H$, which is sufficient to update its position.

% 
% ##     ##   ###    ##     ##    ###      ########  ########  #######   ######  
% ##     ##  ##       ##   ##       ##     ##     ## ##       ##     ## ##    ## 
% ##     ## ##         ## ##         ##    ##     ## ##       ##     ## ##       
% ######### ##          ###          ##    ########  ######   ##     ##  ######  
% ##     ## ##         ## ##         ##    ##   ##   ##       ##  ## ##       ## 
% ##     ##  ##       ##   ##       ##     ##    ##  ##       ##    ##  ##    ## 
% ##     ##   ###    ##     ##    ###      ##     ## ########  ##### ##  ######  
%

\subsection{Requirements for Measurement Model}
% Must be such that Jacobian consists of linear combinations of state-related variables

The requirement introduced above, is that measurement matrix and vector $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ can be computed as linear combinations of functions involving only state vector elements. In particular, a linear combination of functions which depend only on information available to the navigator. In the measurement matrix and vector above, $H$ is the measurement function Jacobian, and includes current state information as well.

As our encryption scheme only supports linear combinations of weights, the weights need to capture all non-linear computations involving state vector elements. From the definition of matrix multiplication, we see that any $KxL$ matrix $D=ABC$, where $B$ has dimensions $MxN$, has element $d_{i,j}$ defined by
\begin{equation*}
    d_{i,j} = \sum^{N}_{n=1}\sum^{M}_{m=1}a_{i,m}b_{m,n}c_{n,j}\,,
\end{equation*}
and can therefore be considered as a linear combination of all elements $a_{i,m}c_{n,j}$. Applying this to the measurement matrix and vector $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$, we require that all values of $h(x)$, and all elements in Jacobian $H$ be linear combinations of functions dependant on state vector elements and nothing else.

We will show how this can be achieved for the specific case of 2-dimensional localisation, with range-only sensors.

\subsection{Localisation Measurement Model} \label{subsec:observation_model}
% Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.

@@

From our problem statement in Section \ref{sec:problem_statement}, we specify the goal of private localisation in the 2-dimensional case, using range-only sensors. Given the current location estimate $x_{loc} = (x,y)$, which may comprise only part of the filter state estimate, and sensor location $s_{loc} = (s_x, s_y)$, the measurement equation is given by
\begin{equation*}
    \begin{split}
        h(x) &= \|x_{loc} - s_{loc}\| \\
        &= \sqrt{(x - s_x)^2 + (y - s_y)^2}\,.
    \end{split}
\end{equation*}
The Jacobian $H$ for the measurement function above at $x_{loc,0}=(x_0, y_0)$ is then given by
\begin{equation*}
    H = 
    \begin{bmatrix}
        \frac{x_0 - s_x}{\sqrt{(x_0 - s_x)^2 + (y_0 - s_y)^2}} \\
        \frac{y_0 - s_y}{\sqrt{(x_0 - s_x)^2 + (y_0 - s_y)^2}} 
    \end{bmatrix}\,.
\end{equation*}
The problem with the above function $h$ and Jacobian $H$ is that they cannot be reformulated as a linear combination of weights, where weights do not depend on $s_x$ and $s_y$.

Our proposed solution to this problem, is working with the adjusted measurement function $h'(x) = h(x)^2$. The method for modifying a normal range-sensor measurement in this way and handling the no-longer Gaussian measurement noise with variance dependant on distance, will be discussed in Section \ref{subsec:range_measurement_mod}. While this transformation complicates the measurement model noise, it allows for the linear formulation required for the encryption scheme, and the privacy of $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$. The adjusted measurement function is now given by
\begin{equation*}
    \begin{split}
        h'(x) &= \left(\|x_{loc} - s_{loc}\|\right)^2 \\
        &= (x - s_x)^2 + (y - s_y)^2 \\
        &= x^2 + y^2 -2s_xx -2s_yy +s_x^2 +s_y^2
    \end{split}\,,
\end{equation*}
and Jacobian $H'$ by
\begin{equation*}
    H' = 
    \begin{bmatrix}
        2x_0 - 2s_x \\
        2y_0 - 2s_y
    \end{bmatrix}\,.
\end{equation*}
The above function and jacobian elements are linear combinations of functions $x$, $x^2$, $y$, $xy$ and $y^2$. From the previous section, we know we can now define $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$ in terms of more state vector dependant functions, in this case, $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$.
\begin{equation*}
    \begin{split}
        H&^{\prime\top} R^{\prime -1}(z' - h(x) + Hx) = \\
        &\begin{bmatrix}
            \begin{split}
                &(2R^{\prime -1}z')x + (-2R^{\prime -1}s_xz) + (-2R^{\prime -1}s_x^2)x \\
                &\quad+ (2R^{\prime -1}s_x^3) + (-2R^{\prime -1}s_y^2)x + (2R^{\prime -1}s_xs_y^2) \\
                &\quad+ (2R^{\prime -1})x^3 + (-R^{\prime -1}s_x)x^2 + (2R^{\prime -1})xy^2 \\
                &\quad+ (-2R^{\prime -1}s_x)y^2
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2R^{\prime -1}z)y + (-2R^{\prime -1}s_yz) + (-2R^{\prime -1}s_x^2)y \\
                &\quad+ (2R^{\prime -1}s_ys_x^2) + (-2R^{\prime -1}s_y^2)y + (2R^{\prime -1}s_y^3) \\
                &\quad+ (2R^{\prime -1})x^2y + (-2R^{\prime -1}s_y)x^2 + (2R^{\prime -1})y^3 \\
                &\quad+ (-2R^{\prime -1}s_y)y^2
            \end{split}
        \end{bmatrix}
    \end{split}
\end{equation*}
and
\begin{equation*}
    H^{\prime\top} R^{\prime -1}H' = 
    \begin{bmatrix}
        \alpha_{11} & \alpha_{12} \\
        \alpha_{21} & \alpha_{22}
    \end{bmatrix}\,,
\end{equation*}
with
\begin{align*}
    \alpha_{11} &= (4R^{\prime -1})x^2 + (-8R^{\prime -1}s_x)x + (4R^{\prime -1}s_x^2) \\
    \begin{split}
        \alpha_{12} &= (4R^{\prime -1})xy + (-4R^{\prime -1}s_y)x + (-4R^{\prime -1}s_x)y \\
        &\qquad+ (4R^{\prime -1}s_xs_y)
    \end{split}\\
    \alpha_{21} &= \alpha_{12} \\
    \alpha_{22} &= (4R^{\prime -1})y^2 + (-8R^{\prime -1}s_y)y + (4R^{\prime -1}s_y^2)\,.
\end{align*}

>>>>

The navigator state is defined as 
\begin{equation}
    \rvec{x} = 
    \begin{bmatrix}
        \rv{x} & \rv{dx} & \rv{y} & \rv{dy}
    \end{bmatrix}^\top\,. \label{eqn:state_def}
\end{equation}
A known process model is followed, which at time $k$ is given by
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
\end{equation}
with zero-mean Gaussian process noise $w_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
\begin{equation}
    \rv{z}_k = h_i(\rvec{x}_k)+\rv{v}_k\,, \label{eqn:measurement_model}
\end{equation}
with noise $\rv{v}_k \sim \mathcal{N}(0,r_i)$, while the measurement function $h_i$, for sensor $i$ at location
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top\,,
\end{equation} 
is defined as
\begin{equation}
    \begin{split}
        h_i(\rvec{x}_k) &= \left\|
        \begin{bmatrix}
            \rv{x}_k & \rv{y}_k
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\| \\
        &= \sqrt{(\rv{x}_k-s_{x,i})^2 + (\rv{y}_k-s_{y,i})^2}\,.
    \end{split}
\end{equation}
We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\rvec{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $\rv{z}_k$ at any time $k$.

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
\begin{equation}
    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \rvec{y}_k = \rvec{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobian
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
\begin{equation}
    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
\end{equation}
and
\begin{equation}
    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_k}\,.
\end{equation}

@@

\section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
Given our definitions for the aggregation scheme in Section \ref{sec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}. We consider a navigator in the presence of $n$ range sensors, running a local filter with update steps computed by equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}. Received information from each sensor $i$ consists of the measurement vector
\begin{equation}
    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
at each time step $k$. In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.

Normal privacy-preserving aggregation encryption of $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors would require the navigator to disclose some location information in $\rvec{x}_k$, for the computing of Jacobians $\mat{H}_{k,i}$. Instead, we want to formulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use an LCAO secure encryption scheme, with location information in $\rvec{x}_k$ as weights from the navigator. As was shown in Section \ref{sec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and the navigator cannot learn individual sensor values $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a reformulation sets requirements on the possible measurement functions $h_i$. As matrix multiplication and scalar multiplication both preserve linearity, it is sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well. Next, we will show how this can be achieved for the specific case of two-dimensional range-only localisation.

\subsection{Localisation Measurement Model} \label{subsec:observation_model}
Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we see that $h_i$ cannot be rearranged to a linear combination of elements private to the navigator. In addition, the Jacobian of $h_i$,
\begin{equation}
    \mat{H}_{k,i} = 
    \begin{bmatrix}
        \frac{\rv{x}_k - s_x}{\sqrt{(\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2}} \\
        \frac{\rv{y}_k - s_y}{\sqrt{(\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2}} 
    \end{bmatrix}\,,
\end{equation}
cannot be either. Instead, we consider the adjusted measurement functions
\begin{equation}
    h'_i(\rvec{x}_k) = h_i(\rvec{x}_k)^2\,. \label{eqn:adjusted_measurement_funcs}
\end{equation}
Measurement functions in this form allow rearrangement of the corresponding adjusted measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ into linear combinations of navigator information.The modified measurement functions $h'_i$ can be written as
\begin{equation}
    \begin{split}
        h'_i(\rvec{x}_k) &= \left\|
        \begin{bmatrix}
            \rv{x}_k & \rv{y}_k
        \end{bmatrix}^\top - \vec{s}_i\right\|^2 \\
        &= (\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2 \\
        &= \rv{x}_k^2 + \rv{y}_k^2 -2s_x\rv{x}_k -2s_y\rv{y}_k +s_x^2 +s_y^2
    \end{split}\,,
\end{equation}
and the corresponding Jacobians $\mat{H}'_{k,i}$ as
\begin{equation}
    \mat{H}'_{k,i} = 
    \begin{bmatrix}
        2\rv{x}_k - 2s_x \\
        2\rv{y}_k - 2s_y
    \end{bmatrix}\,.
\end{equation}
The above have been rearranged as linear combinations of the weights $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which capture all the required information that is private to the navigator.

As stated previously, computing $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ will preserve this ability, albeit increasing the number of weights to include combinations of their products. $\rvec{i}'_{k,i}$ can now be written as
\begin{equation}
    \begin{split}
        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \mean{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
        &= \\
        &\hspace{-1em}
        \begin{bmatrix}
            \begin{split}
                &(2\mean{r}_{k,i}^{-1})\rv{x}_k^3 + (2\mean{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\mean{r}_{k,i}^{-1}s_x)\rv{x}_k^2 \\
                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k + (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{x}_k \\
                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{x}_k + (2\mean{r}_{k,i}^{-1}s_x^3) + (2\mean{r}_{k,i}^{-1}s_xs_y^2) \\
                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x \rv{z}'_{k,i})
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2\mean{r}_{k,i}^{-1})\rv{y}_k^3 + (2\mean{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\mean{r}_{k,i}^{-1}s_y)\rv{x}_k^2 \\
                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k + (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{y}_k \\
                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{y}_k + (2\mean{r}_{k,i}^{-1}s_ys_x^2) + (2\mean{r}_{k,i}^{-1}s_y^3) \\
                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y\rv{z}'_{k,i})
            \end{split}
        \end{bmatrix}
    \end{split}
\end{equation}

\begin{equation}
    \mat{H}_{k,i}^{\prime\top} \mean{r}_{k,i}^{-1}\mat{H}'_{k,i} = 
    \begin{bmatrix}
        \alpha_{11} & \alpha_{12} \\
        \alpha_{21} & \alpha_{22}
    \end{bmatrix}\,,
\end{equation}
with
\begin{align}
    \alpha_{11} &= (4\mean{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\mean{r}_{k,i}^{-1}s_x)\rv{x}_k + (4\mean{r}_{k,i}^{-1}s_x^2) \\
    \begin{split}
        \alpha_{12} &= (4\mean{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\mean{r}_{k,i}^{-1}s_y)\rv{x}_k + (-4\mean{r}_{k,i}^{-1}s_x)\rv{y}_k \\
        &\qquad+ (4\mean{r}_{k,i}^{-1}s_xs_y)
    \end{split}\\
    \alpha_{21} &= \alpha_{12} \\
    \alpha_{22} &= (4\mean{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\mean{r}_{k,i}^{-1}s_y)\rv{y}_k + (4\mean{r}_{k,i}^{-1}s_y^2)\,.
\end{align}

Modification of measurements $z_{k,i}$ to suit the adjusted measurement functions will not preserve the Gaussian nature of the true measurement noise, and will additionally require estimation of the sensor measurement variance $r_i$. We will denote the modified measurement from sensor $i$ at time $k$ as $\rv{z}'_{k,i}$, and the estimated, now time-dependant, sensor variance as $\mean{r}_{k,i}$. The computations of these values will be discussed in Section \ref{subsec:range_measurement_mod}.

@@

% Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.

@@

% The above function and jacobian elements are linear combinations of functions $x$, $x^2$, $y$, $xy$ and $y^2$. From the previous section, we know we can now define $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$ in terms of more state vector dependant functions, in this case, $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$.
% \begin{equation*}
%     \begin{split}
%         H&^{\prime\top} R^{\prime -1}(z' - h(x) + Hx) = \\
%         &\begin{bmatrix}
%             \begin{split}
%                 &(2R^{\prime -1}z')x + (-2R^{\prime -1}s_xz) + (-2R^{\prime -1}s_x^2)x \\
%                 &\quad+ (2R^{\prime -1}s_x^3) + (-2R^{\prime -1}s_y^2)x + (2R^{\prime -1}s_xs_y^2) \\
%                 &\quad+ (2R^{\prime -1})x^3 + (-R^{\prime -1}s_x)x^2 + (2R^{\prime -1})xy^2 \\
%                 &\quad+ (-2R^{\prime -1}s_x)y^2
%             \end{split}
%             \vspace{5pt}\\
%             \begin{split}
%                 &(2R^{\prime -1}z)y + (-2R^{\prime -1}s_yz) + (-2R^{\prime -1}s_x^2)y \\
%                 &\quad+ (2R^{\prime -1}s_ys_x^2) + (-2R^{\prime -1}s_y^2)y + (2R^{\prime -1}s_y^3) \\
%                 &\quad+ (2R^{\prime -1})x^2y + (-2R^{\prime -1}s_y)x^2 + (2R^{\prime -1})y^3 \\
%                 &\quad+ (-2R^{\prime -1}s_y)y^2
%             \end{split}
%         \end{bmatrix}
%     \end{split}
% \end{equation*}
% and
% \begin{equation*}
%     H^{\prime\top} R^{\prime -1}H' = 
%     \begin{bmatrix}
%         \alpha_{11} & \alpha_{12} \\
%         \alpha_{21} & \alpha_{22}
%     \end{bmatrix}\,,
% \end{equation*}
% with
% \begin{align*}
%     \alpha_{11} &= (4R^{\prime -1})x^2 + (-8R^{\prime -1}s_x)x + (4R^{\prime -1}s_x^2) \\
%     \begin{split}
%         \alpha_{12} &= (4R^{\prime -1})xy + (-4R^{\prime -1}s_y)x + (-4R^{\prime -1}s_x)y \\
%         &\qquad+ (4R^{\prime -1}s_xs_y)
%     \end{split}\\
%     \alpha_{21} &= \alpha_{12} \\
%     \alpha_{22} &= (4R^{\prime -1})y^2 + (-8R^{\prime -1}s_y)y + (4R^{\prime -1}s_y^2)\,.
% \end{align*}
